### 2018-08-08 paper/squad-overlay-design.tex
commented out former VD (node selection) due to redundancy and outdated content

%\subsection{Probabilistic Onion Routes}
\subsection{Selection of nodes for routes creation}
\label{ssec:por}

%\subsubsection{The global overlay}
\subsubsection{\GetRandomNode}
\label{sssec:global_overlay}

Devices need to know the address of SPORES participants in order to craft PORs.
To this end, we employ a Random Peer Sampling service~\cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007,Jesi_Montresor_van_Steen_2010} (RPS) among all nodes in SPORES.
It is a gossip protocol that allows each participant to keep a fixed-size \emph{random} subset of other nodes' descriptor (that we will call the RPS's \emph{view} \rpsview). 
The view is constantly evolving, as queries are periodically issued between nodes to exchange descriptors between their respective views.
Finally, offline nodes are quickly evicted from devices' views.

The randomness of the views must be guaranteed: 
a node that would be present in views too often would become a bottleneck, and could monitor a bigger portion of the network.
It will be evaluated in section~\commentAL{TODO}.

In SPORES, a descriptor $\desc_d$ describing device $d$ contains the following information:
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item \(\Pon_d\) is the node's probability of remaining online at the time of the descriptor's creation.
\end{itemize}

$(d, \pk_d, \Pon_d)= \leftarrow \GetRandomNode$ is the function that takes a node from the RPS's view \rpsview on demand.

%\subsubsection{Routes creation}
\subsubsection{\CreateLayer}
\label{sssec:routes_creation}

Routes are created via \Sphinxes as described in section~\ref{sec:SPOR}.
But each layer \layer constituting the route is created by the $\CreateLayer$ function, that is independent from \Sphinxes.

In \name, we wish to maximize the availability of the route.
Therefore, each layer \layer is created so as to reach the availability threshold $\theta$, a parameter chosen by the user.
Note that \Sphinxes is agnostic to this use-case: one could want to maximize other characteristics, e.g. the layer's expected bandwidth.

$\CreateLayer$ iteratively calls $\GetRandomNode\xspace$ to add random nodes to the current layer \layer, until the layer's probability of being offline, $\Poff^\layer$, falls below the availability threshold $\theta$:

$$ \Poff^\layer = \sum\limits_{d \in \layer}(1 - \desc_d.\Pon_d) $$

When a device creates a layer to reach its user, descriptors are not taken from \rpsview but from the \squad's sequence: all devices in this layer will belong to the user.
The logic is otherwise the same.

Recall that each layer in \Sphinxes has a constant number of nodes $w_\layer$, that is a \Sphinxes parameter.
If $w_\layer$ is reached before $\Poff^\layer < \theta$, then we early abort $\CreateLayer$.
On the other hand, if $|\layer| < w_\layer$, we pad the layer with blank descriptors, such that the header always weighs the same size.

>>>>

%\subsection{Probabilistic Onion Routes}
% \subsection{Selection of nodes for routes creation}
% \label{ssec:por}

% %\subsubsection{The global overlay}
% \subsubsection{\GetRandomNode}
% \label{sssec:global_overlay}

% Devices need to know the address of SPORES participants in order to craft PORs.
% To this end, we employ a Random Peer Sampling service~\cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007,Jesi_Montresor_van_Steen_2010} (RPS) among all nodes in SPORES.
% It is a gossip protocol that allows each participant to keep a fixed-size \emph{random} subset of other nodes' descriptor (that we will call the RPS's \emph{view} \rpsview). 
% The view is constantly evolving, as queries are periodically issued between nodes to exchange descriptors between their respective views.
% Finally, offline nodes are quickly evicted from devices' views.

% The randomness of the views must be guaranteed: 
% a node that would be present in views too often would become a bottleneck, and could monitor a bigger portion of the network.
% It will be evaluated in section~\commentAL{TODO}.

% In SPORES, a descriptor $\desc_d$ describing device $d$ contains the following information:
% \begin{itemize}
%   \item \(d\) is the node's identifier (address);
%   \item \(\pk_d\) is the node's public key;
%   \item \(\Pon_d\) is the node's probability of remaining online at the time of the descriptor's creation.
% \end{itemize}

% $(d, \pk_d, \Pon_d)= \leftarrow \GetRandomNode$ is the function that takes a node from the RPS's view \rpsview on demand.

% %\subsubsection{Routes creation}
% \subsubsection{\CreateLayer}
% \label{sssec:routes_creation}

% Routes are created via \Sphinxes as described in section~\ref{sec:SPOR}.
% But each layer \layer constituting the route is created by the $\CreateLayer$ function, that is independent from \Sphinxes.

% In \name, we wish to maximize the availability of the route.
% Therefore, each layer \layer is created so as to reach the availability threshold $\theta$, a parameter chosen by the user.
% Note that \Sphinxes is agnostic to this use-case: one could want to maximize other characteristics, e.g. the layer's expected bandwidth.

% $\CreateLayer$ iteratively calls $\GetRandomNode\xspace$ to add random nodes to the current layer \layer, until the layer's probability of being offline, $\Poff^\layer$, falls below the availability threshold $\theta$:

% $$ \Poff^\layer = \sum\limits_{d \in \layer}(1 - \desc_d.\Pon_d) $$

% When a device creates a layer to reach its user, descriptors are not taken from \rpsview but from the \squad's sequence: all devices in this layer will belong to the user.
% The logic is otherwise the same.

% Recall that each layer in \Sphinxes has a constant number of nodes $w_\layer$, that is a \Sphinxes parameter.
% If $w_\layer$ is reached before $\Poff^\layer < \theta$, then we early abort $\CreateLayer$.
% On the other hand, if $|\layer| < w_\layer$, we pad the layer with blank descriptors, such that the header always weighs the same size.
